Cognitive Context: Impact on the Perception of a Robot

### 2015-07-03 main.tex
Completely removed H1 which does not bring much to the paper

Several hypotheses ensued, our baseline hypothesis \h{0} being that \emph{shallow
cognitive contexts} and \emph{deep cognitive contexts} are recognized
(manipulation check) and interpreted by the participants as being respectively
\emph{machine-like} (low level of anthropomorphic attributions) or
\emph{human-like} (higher level of anthropomorphic attributions).

Our first hypothesis \h{1} is that gaze behaviour alone is sufficient to
know if a subject is looking at a robot or at a human.  More precisely, we
hypothesize that the distribution of gaze fixations on the different body parts
is significantly different when watching a robot or a human performing the same
task.

@@

Participants were asked in the post-questionnaire whether the video presented a
\emph{``robot kind of task''} or a \emph{``human kind of task''} on a 5-points
scale (numerical values ranging from -2 to 2, where -2 refers to robot kind of
task). As can be seen in figure 2, we got a significant correlation in this
manipulation check ($F[1,54] = 29.0, p < .001$) which validates our manipulation
and supports \h{0}: the participants that were shown the \emph{shallow cognitive
context} videos identified the task as more robot-like and participants watching
\emph{deep cognitive context} videos perceived the tasks as more human-like.

\subsection{Gaze differences between human and robot conditions}

We grouped the 8 areas of interest located on the agent into 4 categories : {\sf
head}, {\sf arms} (containing both arms and hands), {\sf torso}, {\sf legs}
(including both legs). Running an ANOVA against gaze fixations on the areas of
interest and the robot \vs human conditions, we obtain the following results:

{\sf head}: the fixations on the head for the human video
were observed to more than that for the robot video ($F[1,54] = 12.7, p < .001$)

{\sf arms}: the fixations on the arms for the $\mathcal{H}$ video
were also greater than that for the robot video ($F[1,54] = 16.5, p < .01$)

{\sf legs}: the fixations on the legs were much lower
for the human video as compared to the robot video ($F[1,54] = 1.9, p < .1$)

{\sf torso}: the fixations on the torso were higher for the
human video than for the robot video ($F[1,54] = 2.65, p < .1$)

In summary, and over the duration of these shorts videos, the gaze behaviours
were significantly different between the robot and human conditions, supporting
\h{1}.

@@

The clearly significant correlation between deep \vs shallow conditions and the
answers to the question \emph{Were the task more robot-like or human-like?}
proves that our manipulation was successful, and that a shallow cognitive
context was indeed associated to a robot-like situation, while a deeper
cognitive context was associated to a human-like situation (\h{0}).

The hypothesis \h{1} postulated that the gaze behaviours alone could tell if the
subjects was observing a robot or a human. Indeed, our results show
significantly different (normalized) fixations: the gaze distribution of a human
observer are different for humans and robots.

>>>>

We actually build several hypotheses: our baseline hypothesis \h{1} being that \emph{shallow
cognitive contexts} and \emph{deep cognitive contexts} are recognized
(manipulation check) and interpreted by the participants as being respectively
\emph{machine-like} (low level of anthropomorphic attributions) or
\emph{human-like} (higher level of anthropomorphic attributions).

@@

Participants were asked in the post-questionnaire whether the video presented a
\emph{``robot kind of task''} or a \emph{``human kind of task''} on a 5-points
scale (numerical values ranging from -2 to 2, where -2 refers to robot kind of
task). As can be seen in figure 2, we got a significant correlation in this
manipulation check ($F[1,54] = 29.0, p < .001$) which validates our manipulation
and supports \h{1}: the participants that were shown the \emph{shallow cognitive
context} videos identified the task as more robot-like and participants watching
\emph{deep cognitive context} videos perceived the tasks as more human-like.

@@

The clearly significant correlation between deep \vs shallow conditions and the
answers to the question \emph{Were the task more robot-like or human-like?}
proves that our manipulation was successful, and that a shallow cognitive
context was indeed associated to a robot-like situation, while a deeper
cognitive context was associated to a human-like situation (\h{1}).
